---
title: "BVI literature review - labelling"
author: "Seewoo Li"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(xlsx)
library(jsonlite)
library(glue)

source("automated_literature_review.R")
```

# Data

```{r data, echo=FALSE}
data <- read.csv("BVI_literature_review_table.csv")
```

# 1. [Yes or No] Is the paper about blindness and visually impaired students (BVI)?

```{r 1, echo=FALSE}
data$Answer.1 %>% 
  table()
```

# 2. [Accommodation or not] Does this paper describe accommodation for students with BVI?

```{r 2, echo=FALSE}
data$Answer.2 %>% 
  table()
```



# 3. [Description of the Tech] What is the accommodation/technology about?

```{r 3, echo=FALSE}
data$Answer.3 %>% 
  knitr::kable(format = "latex")
```


```{r 3-2, echo=FALSE}
labelel_res <- read.csv("BVI_tools_summarized.csv")

labelel_res[-(1:2)] %>% head()
```

## Summary of Answer3

```{r 3-3, echo=FALSE}
colSums(labelel_res[-(1:2)])
```

# 4. [learning vs assessment and classroom vs large scale] Where is this accommodation used?

```{r 4, echo=FALSE}
data$Answer.4 %>% 
  table() %>% 
  as.matrix()
```



# 5. Which grades or levels of education (e.g., elementary, middle school, high school, college, professional, post-graduate)?

```{r 5, echo=FALSE}
data$Answer.5 %>% 
  table() %>% 
  as.matrix()
```



# 6. What’s the sample size of the participants in the accomodation?

```{r 6, echo=FALSE}
data$Answer.6 %>% 
  table() %>% 
  as.matrix()
```

# 7. What country and/or state is the assessment used in?

```{r 7, echo=FALSE}
data$Answer.7 %>% 
  table() %>% 
  as.matrix()
```


# 8. In which subject or area is this accommodation applied to?

```{r 8, echo=FALSE}
data$Answer.8 %>% 
  table() %>% 
  as.matrix()
```


# 9. Is the accommodation actually being used? By how many people?

```{r 9, echo=FALSE}
data$Answer.9 %>% 
  table() %>% 
  as.matrix()
```
